---
title: "R Notebook"
output:
  html_document:
    df_print: paged
Author: Diana Kayser
created: 20200822
last revised: 20200822
---



```{r clear global environment, message=FALSE, include=FALSE}
rm(list = ls(all.names = TRUE)) #clears all variables in global environment
```
```{r load libraries, message=FALSE, warning=FALSE}
library(foreign) #open external files
library(reshape2)
library(beepr)
library(tidyr)
library(tidyverse)
library(stargazer)
library(lme4)
library(afex)
library(ggplot2)
```

```{r load dataset in wide format, message=FALSE, warning=FALSE, include=FALSE}
dataset=read.spss("D:/BBC_PAPER/01BBC_Data/20200827_Experiment3_wide_valid_1.sav", to.data.frame=TRUE)
#copy of dataset just in case
data<-dataset
data$id<-as.factor(data$Participant_No)

```


```{r transform dataset into long format, message=FALSE, warning=FALSE, include=FALSE}
#reshape as we are not going to work with the wide format

library(reshape2)

datalong <- reshape(data,
  varying = 
    c(
      "Debussy_Neutral",
      "Debussy_Happy",
      "Debussy_Sad",
      "Debussy_Anger",
      "Debussy_Surprise",
      "Debussy_Fear",
      "Debussy_Disgust", 
      "Debussy_Preference_1",
      "Debussy_Familiarity_1",
      "Debussy_Valence_1",
      "Debussy_Arousal_1",
      
      "Beethoven_Neutral",
      "Beethoven_Happy",
      "Beethoven_Sad",
      "Beethoven_Anger",
      "Beethoven_Surprise",
      "Beethoven_Fear",
      "Beethoven_Disgust",
      "Beethoven_Preference_2",
      "Beethoven_Familiarity_2",
      "Beethoven_Valence_2",
      "Beethoven_Arousal_2",

      "Chopin_Neutral",
      "Chopin_Happy",
      "Chopin_Sad",
      "Chopin_Anger",
      "Chopin_Surprise",
      "Chopin_Fear",
      "Chopin_Disgust",
      "Chopin_Preference_3",
      "Chopin_Familiarity_3",
      "Chopin_Valence_3",
      "Chopin_Arousal_3",

      "Mozart_Neutral",
      "Mozart_Happy",
      "Mozart_Sad",
      "Mozart_Anger",
      "Mozart_Surprise",
      "Mozart_Fear",
      "Mozart_Disgust",
      "Mozart_Preference_4",
      "Mozart_Familiarity_4",
      "Mozart_Valence_4",
      "Mozart_Arousal_4"
      ), 
  
 v.names = c("a_face_neutral",
             "b_face_happy",
             "c_face_sad",
             "d_face_anger",
             "e_face_surprise",
             "f_face_fear",
             "g_face_disgust",
             "h_rating_preference",
             "i_rating_familiarity",
             "j_rating_pleasantness",
             "k_rating_activation"
             ),
 
 timevar = "piece", 
 
 times = c("Debussy",
           "Beethoven", 
           "Chopin", 
           "Mozart"),  
 
 ids=id, new.row.names = 1:10000, direction = "long")
```



```{r rename variables}
#select variables we need for the analysis as this is quite a big data set
library(dplyr) #select()

datalong_reduced<-datalong %>% 
  select(id, piece, contains(c("face","rating")))

names(datalong_reduced)<-c("id",
        "piece",
        "face_neutral",
        "face_happy",
        "face_sad",
        "face_anger",
        "face_surprise",
        "face_fear",
        "face_disgust",
        "preference",
        "liking",
        "pleasantness",
        "activation"
        )

```


```{r transform dataset into long format, message=FALSE, warning=FALSE, include=FALSE}
#reshape as we are not going to work with the wide format

library(reshape2)

datalongRAW <- reshape(data,
  varying = 
    c(
      "Debussy_Neutral_Raw",
      "Debussy_Happy_Raw",
      "Debussy_Sad_Raw",
      "Debussy_Anger_Raw",
      "Debussy_Surprise_Raw",
      "Debussy_Fear_Raw",
      "Debussy_Disgust_Raw", 
      "Debussy_Preference_1",
      "Debussy_Familiarity_1",
      "Debussy_Valence_1",
      "Debussy_Arousal_1",
      
      "Beethoven_Neutral_Raw",
      "Beethoven_Happy_Raw",
      "Beethoven_Sad_Raw",
      "Beethoven_Anger_Raw",
      "Beethoven_Surprise_Raw",
      "Beethoven_Fear_Raw",
      "Beethoven_Disgust_Raw",
      "Beethoven_Preference_2",
      "Beethoven_Familiarity_2",
      "Beethoven_Valence_2",
      "Beethoven_Arousal_2",

      "Chopin_Neutral_Raw",
      "Chopin_Happy_Raw",
      "Chopin_Sad_Raw",
      "Chopin_Anger_Raw",
      "Chopin_Surprise_Raw",
      "Chopin_Fear_Raw",
      "Chopin_Disgust_Raw",
      "Chopin_Preference_3",
      "Chopin_Familiarity_3",
      "Chopin_Valence_3",
      "Chopin_Arousal_3",

      "Mozart_Neutral_Raw",
      "Mozart_Happy_Raw",
      "Mozart_Sad_Raw",
      "Mozart_Anger_Raw",
      "Mozart_Surprise_Raw",
      "Mozart_Fear_Raw",
      "Mozart_Disgust_Raw",
      "Mozart_Preference_4",
      "Mozart_Familiarity_4",
      "Mozart_Valence_4",
      "Mozart_Arousal_4"
      ), 
  
 v.names = c("a_face_neutral_Raw",
             "b_face_happy_Raw",
             "c_face_sad_Raw",
             "d_face_anger_Raw",
             "e_face_surprise_Raw",
             "f_face_fear_Raw",
             "g_face_disgust_Raw",
             "h_rating_preference",
             "i_rating_familiarity",
             "j_rating_pleasantness",
             "k_rating_activation"
             ),
 
 timevar = "piece", 
 
 times = c("Debussy",
           "Beethoven", 
           "Chopin", 
           "Mozart"),  
 
 ids=id, new.row.names = 1:10000, direction = "long")
```



```{r rename variables}
#select variables we need for the analysis as this is quite a big data set
library(dplyr) #select()

datalong_reducedRAW<-datalongRAW %>% 
  select(id, piece, contains(c("face","rating")))

names(datalong_reducedRAW)<-c("id",
        "piece",
        "face_neutral",
        "face_happy",
        "face_sad",
        "face_anger",
        "face_surprise",
        "face_fear",
        "face_disgust",
        "preference",
        "liking",
        "pleasantness",
        "activation"
        )

```



```{r}

datalong_reduced_stacked <- reshape(datalong_reduced,
  varying = 
    c("face_neutral", 
      "face_happy", 
      "face_sad", 
      "face_anger", 
      "face_surprise", 
      "face_fear", 
      "face_disgust"), 
  
  v.names = "intensity",
  timevar = "facecategory", 
  times = c("face neutral", "face happy", "face sad", "face anger", 
            "face surprise", 
            "face fear", 
            "face disgust"),  
  new.row.names = 1:1000,
  direction = "long")


datalong_reduced_stacked$facecategory<-as.factor(datalong_reduced_stacked$facecategory)
  
  datalong_reduced_stacked$facecategory<-relevel(datalong_reduced_stacked$facecategory, "face neutral")


```

```{r}

datalong_reducedRAW_stacked <- reshape(datalong_reducedRAW,
  varying = 
    c("face_neutral", 
      "face_happy", 
      "face_sad", 
      "face_anger", 
      "face_surprise", 
      "face_fear", 
      "face_disgust"), 
  
  v.names = "intensity",
  timevar = "facecategory", 
  times = c("face neutral", "face happy", "face sad", "face anger", 
            "face surprise", 
            "face fear", 
            "face disgust"),  
  new.row.names = 1:1000,
  direction = "long")



datalong_reducedRAW_stacked$facecategory<-as.factor(datalong_reducedRAW_stacked$facecategory)
  
  datalong_reducedRAW_stacked$facecategory<-relevel(datalong_reducedRAW_stacked$facecategory, "face neutral")

```





```{r fig.height=15, fig.width=20}
library(ggthemes)

size<-25   #fontsize
heading<- 0.5 #0.1    #position of the figure title, (0.5 means middle)
angle<-0

theme_pre<- theme_tufte(base_size = size, base_family = "serif", ticks = TRUE)+
  theme(axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank())+
  theme(axis.title   = element_text(face  = "plain", size = size, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = heading)) +
  theme(axis.text.x = element_text(angle = angle, size = size,  vjust = 0.5))




```

```{r fig.height=20, fig.width=30}

datalong_reducedRAW_stacked_splitpiece<-split(datalong_reducedRAW_stacked,datalong_reducedRAW_stacked$piece)

Deb<-datalong_reducedRAW_stacked_splitpiece$Debussy
Deb$id<-as.factor(Deb$id)
Bet<-datalong_reducedRAW_stacked_splitpiece$Beethoven
Bet$id<-as.factor(Bet$id)

Cho<-datalong_reducedRAW_stacked_splitpiece$Chopin
Cho$id<-as.factor(Cho$id)

Moz<-datalong_reducedRAW_stacked_splitpiece$Mozart
Moz$id<-as.factor(Moz$id)

Debussy<-ggplot(data = Deb, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Debussy")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")


Beethoven<-ggplot(data = Bet, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Beethoven")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")


Chopin<-ggplot(data = Cho, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Chopin")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")

Mozart<-ggplot(data = Moz, 
       aes(x=id, y=intensity, fill=facecategory))+ xlab("Subject ID")+ylab("")+
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+
  ggtitle("Mozart")+
  theme(legend.position = "none")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")



piecepanel<-ggarrange(Debussy, Beethoven, Chopin, Mozart,
                       
ncol = 4, nrow = 1,
                      common.legend = TRUE,legend="right")



#piecepanel #save 1100 x 1500 #1100 x 1100





```

```{r fig.height=10, fig.width=20}

piecepanel2<-ggarrange(Debussy, Beethoven, Chopin, Mozart,
                       
                       ncol = 4, nrow = 1,
                      common.legend = TRUE,legend="right")



piecepanel2 #save 1100 x 1500 #1100 x 1100
```

```{r fig.height=20, fig.width=30}

datalong_reduced_stacked_splitpiece<-split(datalong_reduced_stacked,datalong_reduced_stacked$piece)

Debnorm<-datalong_reduced_stacked_splitpiece$Debussy
Debnorm$id<-as.factor(Debnorm$id)

Betnorm<-datalong_reduced_stacked_splitpiece$Beethoven
Betnorm$id<-as.factor(Betnorm$id)

Chonorm<-datalong_reduced_stacked_splitpiece$Chopin
Chonorm$id<-as.factor(Chonorm$id)

Moznorm<-datalong_reduced_stacked_splitpiece$Mozart
Moznorm$id<-as.factor(Moznorm$id)

Debussynorm<-ggplot(data = Debnorm, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Debussy")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")


Beethovennorm<-ggplot(data = Betnorm, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Beethoven")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")


Chopinnorm<-ggplot(data = Chonorm, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Chopin")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")

Mozartnorm<-ggplot(data = Moznorm, 
       aes(x=id, y=intensity, fill=facecategory))+ 
  geom_bar(stat="identity",alpha=0.8)+
  theme_pre+ggtitle("Mozart")+theme(legend.position = "none")+xlab("Subject ID")+ylab("")+
  coord_flip() + 
  scale_fill_brewer(palette = "Set2")



piecepanel3<-ggarrange(Debussynorm, Beethovennorm, Chopinnorm, Mozartnorm,
                       
                      # ncol = 4, nrow = 1,
                      common.legend = TRUE,legend="right")



piecepanel3 #save 1100 x 1500 #1100 x 1100





```
```{r fig.height=40, fig.width=20}
piecepanel_comb1<-ggarrange(Debussy, Debussynorm,
                            Beethoven,Beethovennorm,
                            Chopin,Chopinnorm,
                            Mozart,Mozartnorm,
                       
                       ncol = 2, nrow = 4,
                      common.legend = TRUE,legend="right")
piecepanel_comb1

```
```{r fig.height=10, fig.width=30}
piecepanel_comb1a<-ggarrange(
                            
                            Debussynorm,Beethovennorm,Chopinnorm,Mozartnorm,
                       
                       ncol = 4, nrow = 1,
                      common.legend = TRUE,legend="right")
#piecepanel_comb1a


piecepanel_comb1aanno<-annotate_figure(
  piecepanel_comb1a,
  top =text_grob( "Normalized Facial Expression Intensity",lineheight=2,vjust=0.4,hjust=0.5,family= "serif",size=40))
piecepanel_comb1aanno

```
```{r fig.height=10, fig.width=30}
piecepanel_comb1b<-ggarrange(Debussy,Beethoven,Chopin,Mozart,
                            
                            
                       
                       ncol = 4, nrow = 1,
                      common.legend = TRUE,legend="right")
#piecepanel_comb1b


piecepanel_comb1banno<-annotate_figure(
  piecepanel_comb1b,
  top =text_grob( "Raw Facial Expression Intensity",lineheight=2,vjust=0.4,hjust=0.5,family= "serif",size=40))
piecepanel_comb1banno

```

```{r some mutation, include=FALSE}

 

datalong_reduced<-mutate(datalong_reduced,
                  time.cont=(ifelse(piece== "Debussy","1", ifelse(piece=="Beethoven","2",ifelse(piece=="Chopin","3","4")))))


datalong_reduced<-mutate(datalong_reduced,
                    emotionexpressed=(ifelse(piece == "Debussy"|piece == "Mozart","1","0"))) #codes sad 0 happy 1




 

datalong_reducedRAW<-mutate(datalong_reducedRAW,
                  time.cont=(ifelse(piece== "Debussy","1", ifelse(piece=="Beethoven","2",ifelse(piece=="Chopin","3","4")))))


datalong_reducedRAW<-mutate(datalong_reducedRAW,
                  emotionexpressed=(ifelse(piece == "Debussy"|piece == "Mozart","1","0"))) #codes sad 0 happy 1

```


```{r z-standardize facial expressions in long format and save to dataset, message=FALSE, warning=FALSE, include=FALSE}

datalong_reduced<-mutate(datalong_reduced,
       Zface_neutral=scale(face_neutral),
       Zface_happy = scale(face_happy),
       Zface_sad = scale(face_sad),
       Zface_anger = scale(face_anger),
       Zface_surprise = scale(face_surprise),
       Zface_fear=scale(face_fear),
       Zface_disgust = scale(face_disgust),
       Zrating_activation = scale(activation),
       Zrating_pleasantness = scale(pleasantness))

datalong_reducedRAW<-mutate(datalong_reducedRAW,
       Zface_neutral=scale(face_neutral),
       Zface_happy = scale(face_happy),
       Zface_sad = scale(face_sad),
       Zface_anger = scale(face_anger),
       Zface_surprise = scale(face_surprise),
       Zface_fear=scale(face_fear),
       Zface_disgust = scale(face_disgust),
       Zrating_activation = scale(activation),
       Zrating_pleasantness = scale(pleasantness))

#datalong$Zneutral_face<-scale(datalong$a_face_neutral)
#datalong$Zhappy_face<-scale(datalong$b_face_happy)
#datalong$Zsad_face<-scale(datalong$c_face_sad)
#datalong$Zanger_face<-scale(datalong$d_face_anger)
#datalong$Zsurprise_face<-scale(datalong$e_face_surprise)
#datalong$Zfear_face<-scale(datalong$f_face_fear)
#datalong$Zdisgust_face<-scale(datalong$g_face_disgust)

```


The model does not include piece as a random effect as grouping factors should have at least six different levels (Singnmann et al. 2019, Bolker, 2015) we only have four pieces and and when I included an intercept for 'piece' the variance for that random effect was zero It has further been stated that random effects with a low number of levels can not only lead to problems with the estimation process, but als have detrimental effects on statistical power (see Westfall, Kenny, & Judd, 2014)

p.17

Statistical power: We have not conducted a power analysis as for linear mixed models these are not as straightforward and not implemented in software solutions like GPower. Only recently a method has been introduced,
Simmons, Nelson, and Simonsohn (2011) recommend that each between-subjects condition should have at least 20 participants; singmann et al recommend 20 levels for each random effects grouping factor. As our grouping factor are the participants and we have 27 we assume that power is high enough


```{r fit models Zface neutral, message=FALSE}
library(pbkrtest)
#change fixed factor to 0 and 1 for contrasts
set_sum_contrasts() 

#fitting the nullmodel
m0.3.faceintensity_neutralface_fin<-lmer(Zface_neutral~(0+emotionexpressed|id),
                                                data=datalong_reduced, REML=FALSE) 

#fitting the full model
m1.3.faceintensity_neutralface_fin<-lmer(Zface_neutral~1+emotionexpressed+                                  (0+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#fitting the full model with gender
m1.3.faceintensity_neutralface_fin<-lmer(Zface_neutral~1+emotionexpressed+                                  (0+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 


#saving the model 
m1.3.faceintensity_neutralface_fin.fit<-summary(m1.3.faceintensity_neutralface_fin)
m1.3.faceintensity_neutralface_fin.fit


#save predicted values
datalong_reduced$m1.3.faceintensity_neutralface_fin.predicted<-predict(m1.3.faceintensity_neutralface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_neutralface_fin.confidence<-confint(m1.3.faceintensity_neutralface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_neutralface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_neutralface_fin.anova<-anova(m0.3.faceintensity_neutralface_fin, m1.3.faceintensity_neutralface_fin,test = "LRT")
print(faceintensity_neutralface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_neutralface_fin,
                  m1.3.faceintensity_neutralface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )



#LRT_faceintensity_neutralface_fin<-drop1(m1.3.faceintensity_neutralface_fin,test="Chisq")
#print(LRT_faceintensity_neutralface_fin)

KRmodcomp_faceintensity_neutralface_fin<-KRmodcomp(m0.3.faceintensity_neutralface_fin,m1.3.faceintensity_neutralface_fin)
print(KRmodcomp_faceintensity_neutralface_fin)
library(performance)

#get rsquare
rcompanion::nagelkerke(m1.3.faceintensity_neutralface_fin,m0.3.faceintensity_neutralface_fin)
m1.3.faceintensity_neutralface_fin.r2nakagawa<-r2_nakagawa(m1.3.faceintensity_neutralface_fin)
m1.3.faceintensity_neutralface_fin.r2nakagawa

anova(m1.3.faceintensity_neutralface_fin)

```


```{r fit models Zface happy, echo=TRUE, message=FALSE}
#library(afex)

#fitting the null model
m0.3.faceintensity_happyface_fin<-lmer(Zface_happy~(0+emotionexpressed|id), data=datalong_reduced, REML=FALSE) 

#fitting the full model
m1.3.faceintensity_happyface_fin<-lmer(Zface_happy~1+emotionexpressed+                                  (1+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_happyface_fin.fit<-summary(m1.3.faceintensity_happyface_fin)
m1.3.faceintensity_happyface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_happyface_fin.predicted<-predict(m1.3.faceintensity_happyface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_happyface_fin.confidence<-confint(m1.3.faceintensity_happyface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_happyface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_happyface_fin.anova<-anova(m0.3.faceintensity_happyface_fin, m1.3.faceintensity_happyface_fin,test = "LRT")
print(faceintensity_happyface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_happyface_fin,
                  m1.3.faceintensity_happyface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )



#LRT_faceintensity_neutralface_fin<-drop1(m1.3.faceintensity_neutralface_fin,test="Chisq")
#print(LRT_faceintensity_neutralface_fin)

KRmodcomp_faceintensity_happyface_fin<-KRmodcomp(m0.3.faceintensity_happyface_fin,m1.3.faceintensity_happyface_fin)
print(KRmodcomp_faceintensity_happyface_fin)

rcompanion::nagelkerke(m1.3.faceintensity_happyface_fin,m0.3.faceintensity_happyface_fin)


anova(m1.3.faceintensity_happyface_fin)


```

```{r fit models Zface sad, message=FALSE}
#fitting the null model
m0.3.faceintensity_sadface_fin<-lmer(Zface_sad~(1+emotionexpressed|id), data=datalong_reduced, REML=FALSE) 

#fitting the model
m1.3.faceintensity_sadface_fin<-lmer(Zface_sad~1+emotionexpressed+                                  (1+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_sadface_fin.fit<-summary(m1.3.faceintensity_sadface_fin)
m1.3.faceintensity_sadface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_sadface_fin.predicted<-predict(m1.3.faceintensity_sadface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_sadface_fin.confidence<-confint(m1.3.faceintensity_sadface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_sadface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_sadface_fin.anova<-anova(m0.3.faceintensity_sadface_fin, m1.3.faceintensity_sadface_fin,test = "LRT")
print(faceintensity_sadface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_sadface_fin,
                  m1.3.faceintensity_sadface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )




#LRT_faceintensity_neutralface_fin<-drop1(m1.3.faceintensity_neutralface_fin,test="Chisq")
#print(LRT_faceintensity_neutralface_fin)

KRmodcomp_faceintensity_sadface_fin<-KRmodcomp(m0.3.faceintensity_sadface_fin,m1.3.faceintensity_sadface_fin)
print(KRmodcomp_faceintensity_sadface_fin)

rcompanion::nagelkerke(m1.3.faceintensity_sadface_fin,m0.3.faceintensity_sadface_fin)

anova(m1.3.faceintensity_sadface_fin)


```

```{r fit models Zface anger, message=FALSE}
#fitting the null model 

m0.3.faceintensity_angerface_fin<-lmer(Zface_anger~(0+emotionexpressed|id), data=datalong_reduced, REML=FALSE) 


#fitting the model
m1.3.faceintensity_angerface_fin<-lmer(Zface_anger~1+emotionexpressed+                                  (0+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_angerface_fin.fit<-summary(m1.3.faceintensity_angerface_fin)
m1.3.faceintensity_angerface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_angerface_fin.predicted<-predict(m1.3.faceintensity_angerface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_angerface_fin.confidence<-confint(m1.3.faceintensity_angerface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_angerface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_angerface_fin.anova<-anova(m0.3.faceintensity_angerface_fin, m1.3.faceintensity_angerface_fin,test = "LRT")
print(faceintensity_angerface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_angerface_fin,
                  m1.3.faceintensity_angerface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )



KRmodcomp_faceintensity_angerface_fin<-KRmodcomp(m0.3.faceintensity_angerface_fin,m1.3.faceintensity_angerface_fin)
print(KRmodcomp_faceintensity_angerface_fin)


anova(m1.3.faceintensity_angerface_fin)

```

```{r fit models Zface surprise, message=FALSE}


#fitting the null model
m0.3.faceintensity_surpriseface_fin<-lmer(Zface_surprise~(0+emotionexpressed|id), data=datalong_reduced, REML=FALSE) 


#fitting the model
m1.3.faceintensity_surpriseface_fin<-lmer(Zface_surprise~1+emotionexpressed+                                  (0+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_surpriseface_fin.fit<-summary(m1.3.faceintensity_surpriseface_fin)
m1.3.faceintensity_surpriseface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_surpriseface_fin.predicted<-predict(m1.3.faceintensity_surpriseface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_surpriseface_fin.confidence<-confint(m1.3.faceintensity_surpriseface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_surpriseface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_surpriseface_fin.anova<-anova(m0.3.faceintensity_surpriseface_fin, m1.3.faceintensity_surpriseface_fin,test = "LRT")
print(faceintensity_surpriseface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_surpriseface_fin,
                  m1.3.faceintensity_surpriseface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )




KRmodcomp_faceintensity_surpriseface_fin<-KRmodcomp(m0.3.faceintensity_surpriseface_fin,m1.3.faceintensity_surpriseface_fin)
print(KRmodcomp_faceintensity_surpriseface_fin)
rcompanion::nagelkerke(m1.3.faceintensity_surpriseface_fin,m0.3.faceintensity_surpriseface_fin)

anova(m1.3.faceintensity_surpriseface_fin)


```

```{r fit models Zface fear, message=FALSE}
#fitting the null model
m0.3.faceintensity_fearface_fin<-lmer(Zface_fear~(0+emotionexpressed|id), data=datalong_reduced, REML=FALSE) 


#fitting the model
m1.3.faceintensity_fearface_fin<-lmer(Zface_fear~1+emotionexpressed+                                  (0+emotionexpressed|id),data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_fearface_fin.fit<-summary(m1.3.faceintensity_fearface_fin)
m1.3.faceintensity_fearface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_fearface_fin.predicted<-predict(m1.3.faceintensity_fearface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_fearface_fin.confidence<-confint(m1.3.faceintensity_fearface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_fearface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_fearface_fin.anova<-anova(m0.3.faceintensity_fearface_fin, m1.3.faceintensity_fearface_fin,test = "LRT")
print(faceintensity_fearface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_fearface_fin,
                  m1.3.faceintensity_fearface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )



KRmodcomp_faceintensity_fearface_fin<-KRmodcomp(m0.3.faceintensity_fearface_fin,m1.3.faceintensity_fearface_fin)
print(KRmodcomp_faceintensity_fearface_fin)

rcompanion::nagelkerke(m1.3.faceintensity_fearface_fin,m0.3.faceintensity_fearface_fin)

anova(m1.3.faceintensity_fearface_fin)


```

```{r fit models Zface disgust}
#fitting the null model
m0.3.faceintensity_disgustface_fin<-lmer(Zface_disgust~(0+emotionexpressed|id), data=datalong_reduced, REML=FALSE)


#fitting the model
m1.3.faceintensity_disgustface_fin<-lmer(Zface_disgust~
                                           1+emotionexpressed+ 
                                           (0+emotionexpressed|id),
                                          data=datalong_reduced,REML=FALSE) 

#saving the model 
m1.3.faceintensity_disgustface_fin.fit<-summary(m1.3.faceintensity_disgustface_fin)
m1.3.faceintensity_disgustface_fin.fit

#save predicted values
datalong_reduced$m1.3.faceintensity_disgustface_fin.predicted<-predict(m1.3.faceintensity_disgustface_fin)

#get confidence intervals with Wald method
m1.3.faceintensity_disgustface_fin.confidence<-confint(m1.3.faceintensity_disgustface_fin,method="Wald", level=0.95)
print(m1.3.faceintensity_disgustface_fin.confidence)

#Likelihood Ratio Test against null model
faceintensity_disgustface_fin.anova<-anova(m0.3.faceintensity_disgustface_fin, m1.3.faceintensity_disgustface_fin,test = "LRT")
print(faceintensity_disgustface_fin.anova)

sjPlot::tab_model(m0.3.faceintensity_disgustface_fin,
                  m1.3.faceintensity_disgustface_fin,show.stat=TRUE,show.df=TRUE, p.val = "satterthwaite", show.ci = 0.95  )



KRmodcomp_faceintensity_disgustface_fin<-KRmodcomp(m0.3.faceintensity_disgustface_fin,m1.3.faceintensity_disgustface_fin)
print(KRmodcomp_faceintensity_disgustface_fin)


rcompanion::nagelkerke(m1.3.faceintensity_disgustface_fin,m0.3.faceintensity_disgustface_fin)

anova(m1.3.faceintensity_disgustface_fin)


```



```{r}

datalong_observed <- reshape(datalong_reduced,
  varying = 
    c("face_neutral", 
      "face_happy", 
      "face_sad", 
      "face_anger", 
      "face_surprise", 
      "face_fear", 
      "face_disgust"), 
  
  v.names = "observedvalues",
  timevar = "facecategory", 
  times = c("face neutral", "face happy", "face sad", "face anger", 
            "face surprise", 
            "face fear", 
            "face disgust"),  
  new.row.names = 1:1000,
  direction = "long")





```





```{r}

datalong_predicted <- reshape(datalong_reduced,
  varying = 
    c("m1.3.faceintensity_neutralface_fin.predicted", 
      "m1.3.faceintensity_happyface_fin.predicted", 
      "m1.3.faceintensity_sadface_fin.predicted", 
      "m1.3.faceintensity_angerface_fin.predicted", 
      "m1.3.faceintensity_surpriseface_fin.predicted", 
      "m1.3.faceintensity_fearface_fin.predicted", 
      "m1.3.faceintensity_disgustface_fin.predicted"), 
  
  v.names = "predictedvalues",
  timevar = "facecategory", 
  times = c("face neutral", "face happy", "face sad", "face anger", 
            "face surprise", 
            "face fear", 
            "face disgust"),  
  new.row.names = 1:1000,
  direction = "long")





```

```{r fig.height=10, fig.width=20}
#conditional variable to make highlighting possible

size<-30   #fontsize
heading<- 0.025 #0.1    #position of the figure title, (0.5 means middle)
angle<-0
 library(ggpubr)  
library(ggplot2)

 library(ggthemes)

theme_pre<- theme_tufte(base_size = size, base_family = "serif", ticks = TRUE)+
  theme(axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank())+
  theme(axis.title   = element_text(face  = "plain", size = size, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = heading)) +
  theme(axis.text.x = element_text(angle = angle, size = size,  vjust = 0.5))



datalong_predicted<-mutate(datalong_predicted,
                  face_boxplot=(ifelse(facecategory== "face happy","Y", ifelse(facecategory=="face sad","Y", "N")))) 

my_comparisons <- list( c("Happy", "Sad") )

#splitdata<-as.data.frame(split(datalong, datalong$facecategory))



predictedvalues.plot<-ggplot(datalong_predicted,
                                      aes(x=emotionexpressed,
                                          y=predictedvalues,
                                          #color="grey",
                                         # facet.by="facecategory",
                                          fill=face_boxplot,
                                          alpha=face_boxplot
                                          ))+
  geom_violin()+
    geom_boxplot(width=0.1, color="black", fill="white",alpha=0.9)+
    
  ylim(-3.0,1.5)+
 facet_grid(cols=vars(facecategory))+
  
scale_fill_manual(values=c("grey","#69b3a2"))+

 scale_alpha_manual(values=c(0.3,0.8)) +
  theme_pre+
  theme(legend.position = "none") +
  xlab("emotion expressed") +
  ylab("predicted values")+  
  #coord_flip() + 

 
  ggtitle("")

 

 
predictedvalues.plot



```


```{r transform into longlong format for analysis 1, eval=FALSE, include=FALSE}

datalong_face <- reshape(datalong_reduced,
  varying = 
    c("face_neutral", 
      "face_happy", 
      "face_sad", 
      "face_anger", 
      "face_surprise", 
      "face_fear", 
      "face_disgust"), 
  
  v.names = "faceintensity",
  timevar = "facecategory", 
  times = c("face_neutral", "face_happy", "face_sad", "face_anger", 
            "face_surprise", 
            "face_fear", 
            "face_disgust"),  
  new.row.names = 1:1000,
  direction = "long")

```



```{r Z standardise values for faceintensity, eval=FALSE, include=FALSE}
datalong_face$Zfaceintensity<-scale(datalong_face$faceintensity)
datalong_face$Zactivation<-scale(datalong_face$activation)
datalong_face$Zpleasantness<-scale(datalong_face$pleasantness)
```



```{r fff}
library(lme4)

m0.0.null_activation_full<-lmer(Zactivation~
                             1+
                       (1|id), data=datalong_reduced, REML=FALSE)

summary(m0.1.null_activation_full)

m0.1.null_activation_full<-lmer(Zactivation~
                             1+
                               (1+Zface_neutral)+
                         (1+Zface_happy)+ 
                        (1+Zface_sad)+
                        (1+Zface_anger)+
                        (1+Zface_surprise)+
                        (1+Zface_fear)+
                        (1+Zface_disgust)+
                       (1|id), data=datalong_reduced, REML=FALSE)

summary(m0.1.null_activation_full)

m1.1.activation_full<-lmer(Zactivation~
                             1+
                       (1+Zface_neutral)+
                         (1+Zface_happy)+ 
                        (1+Zface_sad)+
                        (1+Zface_anger)+
                        (1+Zface_surprise)+
                        (1+Zface_fear)+
                        (1+Zface_disgust)+
                       (1|id), data=datalong_reduced, REML=FALSE)

summary(m1.1.activation_full)

rcompanion::nagelkerke(m1.1.activation_full,m0.1.null_activation_full)

anova(m0.0.null_activation_full, m1.1.activation_full)

# effect by participant 
ggplot(data = df.simpson,
       mapping = aes(x = x,
                     y = y,
                     color = participant,
                     group = participant)) +
  geom_point() +
  geom_smooth(method = "lm",
              color = "black") +
  theme(legend.position = "none")
```

